Plasticity of ecophysiological traits structure how herbaceous plant lineages persist in shaded environments 

### 2021-09-27 manuscript/manuscript.Rmd
ran lettuce here, need to create new project!

Ferns and angiosperms growing in low-light habitats had similar A~n~, however, in open habitats angiosperms had 74.0 % higher rates of A~n~ than ferns (canopy x plant group, *P* = 0.043, Figure `r interfig`A). Rates of A~n~ for angiosperms in open habitats were 154.2 % higher than angiosperms in closed habitats (*P* =0.001, t=-4.742), while rates of A~n~ for ferns were statistically similar across habitat types. Overall, ferns and angiosperms in open habitats had nearly 3-fold higher g~s~ than comparable species in closed habitats (*P* = 0.003). Rates of g~s~ for angiosperms in open habitats increased nearly two-fold compared to angiosperms in closed habitats (*P* = 0.0341, t=-2.973), while rates of g~s~ for ferns were statistically similar across habitat types (Figure `r interfig`B). Neither ferns nor angiosperms differed in WUE across the open and closed habitats, and WUE was  statistically similar bewteen the two plant groups.

@@

\
In closed canopy habitats, the LCP of spore-bearing plant species were equivalent and 161.9 % higher than angiosperm species (*P* = 0.0195, Figure `r seedsporefig`C). Photosynthetic quantum was statistically similar between each plant group, but lycophytes and ferns were broadly higher than angiosperms. Spore-bearing plant species had equivalent R~d~, and R~d~ was nearly 4-fold lower than in angiosperms (*P* = 0.0178, Figure `r seedsporefig`D)

>>>>

Ferns and angiosperms growing in low-light habitats had similar A~n~, however, in open habitats angiosperms had 74.0 % higher rates of A~n~ than ferns (canopy x plant group, *P* = 0.043, Figure `r interfig`A). Rates of A~n~ for angiosperms in open habitats were 154.2 % higher than angiosperms in closed habitats (*P* =0.001, t=-4.742), while rates of A~n~ for ferns were statistically similar across habitat types. Overall, ferns and angiosperms in open habitats had nearly 3-fold higher g~s~ than comparable species in closed habitats (*P* = 0.003). Rates of g~s~ for angiosperms in open habitats increased nearly two-fold compared to angiosperms in closed habitats (*P* = 0.0341, t=-2.973), while rates of g~s~ for ferns were statistically similar across habitat types (Figure `r interfig`B). Neither ferns nor angiosperms differed in WUE across the open and closed habitats, and WUE was  statistically similar between the two plant groups.

@@

\
In closed canopy habitats, the LCP of spore-bearing plant species were equivalent and 161.9 % higher than angiosperm species (*P* = 0.0195, Figure `r seedsporefig`C). Photosynthetic quantum yield was statistically similar between each plant group, but lycophytes and ferns were broadly higher than angiosperms. Spore-bearing plant species had equivalent R~d~, and R~d~ was nearly 4-fold lower than in angiosperms (*P* = 0.0178, Figure `r seedsporefig`D)
